%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{microtype}
%\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
%\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{-}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\hypersetup{
  pdftitle=CV/Resume \textbar{} Haluk Dogan,
  pdfauthor=Haluk Dogan,
  pdfsubject=CV/Resume%
}

\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize Last updated on #1\\}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ----------HEADING-----------------
\updateinfo
\vspace{0.5cm}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\Huge Haluk Dogan} & Email : \href{mailto:hdogan@vivaldi.net}{hdogan@vivaldi.net}\\
	\href{https://haluk.github.io/}{https://haluk.github.io/} & Mobile : +1 (531) 218-8301\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Nebraska-Lincoln}{Lincoln, NE}
{Doctor of Philosophy in Computer Science (PhD Candidate)}{August 2018--May 2021}
\resumeSubheading
{Bogazici University}{Istanbul, Turkey}
{Master of Science in Computer Engineering}{September 2011--June 2013}
\resumeSubheading
{Istanbul Bilgi University}{Istanbul, Turkey}
{Bachelor of Science in Computer Science}{September 2006--June 2010}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading{University of Nebraska-Lincoln}{Lincoln, NE} {Machine Learning Scientist}{Aug 2018--Present}
\resumeItemListStart
\resumeItem{Teaching} {I was the head TA of \textbf{``Python Programming for Data
    Science''} courses offered to undergraduate and graduate students. I led
  recitations, lab sessions, and graded weekly assignments.}
\resumeItem{Research} {I work on machine learning with focus on graphical models
  and Bayesian statistics. I have 9 journal, conference, book chapter, and
  preprint publications. I develop my programs for my research in
  \textbf{Python, R}, and \textbf{Java}. I use various third-party programming
  libraries including but not limited to \textbf{TensorFlow} and
  \textbf{Scikit-learn}. I use \textbf{Git} and \textbf{Docker} to share my
  programs and environment for reproducibility. I use UNL's supercomputers and
  \textbf{GCP}.}
\resumeItemListEnd

\resumeSubheading
{Roomkita}{Istanbul, Turkey}
{Co-founder}{Aug 2013--Aug 2019}
\resumeItemListStart
\resumeItem{Developer}
{I helped to develop the website in \textbf{Django}. I also implemented a \textbf{machine learning} module to amend search results. The company is featured in \textbf{tnooz}, a global provider of news related to travel technology.}
\resumeItemListEnd

\resumeSubheading
{Istanbul Bilgi University}{Istanbul, Turkey}
{Research Scientist}{Nov 2010--Aug 2013}
\resumeItemListStart
\resumeItem{Teaching}
{I was the head TA of programming, taught in \textbf{Scheme}, probability and statistics courses. I led lab sessions and graded quizzes, assignments and exams.}
\resumeItem{Software Developer}
{I helped to build the engineering faculty website. Website was in \textbf{Wordpress} but I made customizations in \textbf{PHP} to the CMS and the theme according to our needs.}
\resumeItemListEnd

\resumeSubheading
{i2i Systems}{Istanbul, Turkey}
{Software Developer}{Mar 2010--June 2010}
\vspace{0.1cm}
\resumeItemListStart
{I developed a command-line \textbf{Java} program for PL/SQL developers in the company. Business analysts were preparing the billing rules in spreadsheets. Spreadsheets were unstructured and contained references. Therefore they were not suitable for parsing them as a delimited file. I built the grammar of billing rules using \textbf{JavaCC} and developed its parser. I used \textbf{Spring Framework} and \textbf{Hibernate} to insert rule formulas as a text into the respected database tables. I used \textbf{Maven} to create a jar file of my program. I also create a \textbf{cron} job to run my program in a regular basis.}
\resumeItemListEnd

\resumeSubheading
{GNA}{Istanbul, Turkey}
{Data Scientist}{Aug 2009--Mar 2010}
\vspace{0.1cm}
\resumeItemListStart
{My responsibilities were data staging, data cleaning, and prepare weekly reports. I used \textbf{SQL, Oracle SQL Developer} in my daily routine tasks.}
\resumeItemListEnd

\resumeSubheading
{Aradiom}{Istanbul, Turkey}
{Software Developer}{Mar 2008--Jun 2008}
\vspace{0.1cm}
\resumeItemListStart
{I designed and implemented backend/frontend regex editor to create cron jobs. This was designed for non-technical users. I used \textbf{JBoss Seam Framework}.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Side Projects}
{Implemented and designed a distributed application that sends SMS messages by connecting to SMSC via SMPP by using \textbf{Apache Thrift RPC Framework}}
\vspace{0.1cm}
\resumeSubItem{Course Projects}
{Machine learning algorithms, IO-efficient algorithms, string matching algorithms, data compression algorithms}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: Java, Python, R, Clojure, Lisp, Scheme, SQL}
      }
\item{
            \textbf{Technologies}{: Git, Docker, Maven, Leiningen, Make, Linux, AWK, sed, Emacs}
      }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
